draft

### 2020-02-26 src/draft.Rmd
Update draft.Rmd
aggregated assessment and tax
Update draft.Rmd
imputed tax 2019 by avg of 2016 and 2018 tax pct

## R Markdown
```{r}
library(tidyverse)
```

1. read the data and aggregate them
```{r}
tax_pct<-read_csv(here("data", "tax_pct.csv"))
assessment_pct<-read_csv(here("data", "assessment_pct.csv"))
# omit 2016
assessment_pct<-na.omit(assessment_pct)

>>>>

## R Markdown
```{r}
library(tidyverse)
library(dplyr)
library(here)
library(readxl)
```

1. read the data and aggregate them
```{r}
tax_pct<-read_csv(here("data", "tax_pct.csv"))
assessment_pct<-read_csv(here("data", "assessment_pct.csv"))
# omit 2016
assessment_pct<-na.omit(assessment_pct)
assessment_pct<-assessment_pct[,-c(1)]
names(assessment_pct)[2]<-paste("Municipalities")
tax_pct<-tax_pct[,-c(1)]
